Summary Tables

### 2021-06-01 summary_tables.Rmd
Update propensities

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 95.8|23.8|1.7 |
| cycle | 0.6|0.5|0.2 |
| car | 0.8|16.3|20.6 |
| motorcycle | 0.0|0.0|3.1 |
| bus | 2.4|47.1|62.9 |

>>>>

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 95.8|23.8|1.7 |
| cycle | 0.6|0.5|0.2 |
| car | 0.8|16.3|20.6 |
| motorcycle | 0.0|0.0|3.1 |
| bus | 2.4|47.2|62.9 |
